ST563 Final Project

### 2021-04-20 DRAFT.Rmd
Output MLR model summary to nicer-looking table.

# Load necessary libraries
library(tidyverse) # so many things
library(knitr) # making nice tables
library(caret) # training models & CV
library(leaps) # subset selection
library(corrplot) # visualize correlation
library(rmarkdown) # for output documents
library(randomForest) # fitting random forest model
library(kableExtra) # making bolded headers for tables
library(gridExtra) # stitching graphs together
library(tree) # fitting the classification tree

@@

```{r mlr}
#### REGRESSION ####
lm.reg <- lm(quality ~ volatile.acidity + chlorides + pH + total.sulfur.dioxide + sulphates + alcohol, data = trn)
summary(lm.reg)

@@

The adjusted R-squared value 0.3633 suggests that these six predictors combined explain about 36.33% of the variance in `quality` of a wine.

>>>>

# Load necessary libraries
library(tidyverse) # so many things
library(knitr) # making nice tables
library(caret) # training models & CV
library(leaps) # subset selection
library(corrplot) # visualize correlation
library(rmarkdown) # for output documents
library(randomForest) # fitting random forest model
library(kableExtra) # making bolded headers for tables
library(gridExtra) # stitching graphs together
library(tree) # fitting the classification tree
library(jtools) # for outputting nice-looking model summaries

@@

```{r mlr}
#### REGRESSION ####
lm.reg <- lm(quality ~ volatile.acidity + chlorides + pH + total.sulfur.dioxide + sulphates + alcohol, data = trn)
summ(lm.reg, digits = 3)

@@

The adjusted R-squared value 0.363 suggests that these six predictors combined explain about 36.3% of the variance in `quality` of a wine.
